\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-10-25 manuscript.Rnw
Add cost + QALYs to iCTSTM theory section

>>>>

Costs and QALYs are computed using the continuous time present value given a flow of state values, which change as patients transition between health states or as costs vary as a function of time. The state values can be partitioned into $M$ time intervals indexed by $m = 1,\ldots, M$ where interval $m$ contains times $t$ such that $t_m\leq t \leq t_{m+1}$ and values for state $h$ are equal to $z_{hm}$ during interval $m$. $z_{hm}$ will equal zero during time intervals in which a patient is not in state $h$. Discounted costs and QALYs for health state $h$ are then given by,

\begin{equation}
\sum_{m = 1}^M \int_{t_m}^{t_m+1} z_{hm}e^{-rt}dt = \sum_{m = 1}^M z_{hm} \left(\frac{e^{-r{t_{m}}} - e^{-r{t_{m+1}}}}{r}\right),
\end{equation}

where $r > 0$ is again the discount rate. If $r = 0$, then the present value simplifies to $\sum_{m = 1}^M z_{hm}(t_{m+1} - t_{m})$.

Note that while state values in cohort models can depend on time since the start of the model, state values in individual-level models can depend on either time since the start of the model or time since entering the most recent health state. Individual-level models consequently not only afford more flexibility than cohort models when simulating disease progression, but when simulating costs and/or QALYs as well.
